supplementary plots

### 2024-04-11 04b_supplementary_plots.Rmd

```{r}
targets_ts <- targets |> 
  filter(year(datetime) < 2023) |> 
  ggplot(aes(x=datetime, y=variable, colour = variable)) +
  geom_point(show.legend = F) +
  facet_wrap(~site_id, ncol = 5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

>>>>

```{r}
targets_ts <- targets |> 
  filter(year(datetime) < 2023,
         site_id %in% lake_sites) |> 
  ggplot(aes(x=datetime, y=variable, colour = variable)) +
  geom_point(show.legend = F) +
  facet_wrap(~site_id, ncol = 3) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
